### 2025-12-02 Scripts/Manuscript/manuscript.Rmd
November manuscript rewrites.

---
title             : "Measurement Reliabily, Validity, and Reporting in Replicaitons and Original Research"
shorttitle        : "Measurement Reliability, Validity, and Reporting"

@@

abstract: |
  For a replication to be informative, measurement should be reliable and valid in both original and replication studies.

keywords          : "reliability, construct validity, measurement, reporting, questionable measurement practices, replications, informative replications, psychology"
wordcount         : "1"

@@

floatsintext      : yes
linenumbers       : no
draft             : no
mask              : no

@@

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"

@@

The challenge with measurement in quantitative psychological research is that unlike height or weight, psychological constructs cannot be directly measured, as they cannot be directly observed. Instead, we use scores from a measurement as an indicator for a psychological construct. Yet, it cannot simply be assumed that any measure will form a good indicator of the constructs of interest. The measure has to be validated by establishing the reliability and construct validity of the measure. "Reliability refers to the consistency of scale scores when a construct is assessed multiple times or in multiple ways" [@crutzenScaleQualityAlpha2017b; pp. 244]. Meanwhile, construct validity refers to whether the variance in the measured item scores between participants can be attributed to the variance in the unobserved construct(s) of interest between participants [@cronbachConstructValidityPsychological1955; @vazireCredibilityReplicabilityImproving2022].

However, research indicates that measures often lack reliability and construct validity evidence !!!CITE!!!, either because the evidence is not reported, or because the measures are not validated. @flakeMeasurementSchmeasurementQuestionable2020 dubbed these practices - that raise doubts about a measurement’s validity - Questionable Measurement Practices (QMPs), being a term analogous to Questionable Research Practices [QRPs; Simmons et al. (2011); John et al. (2012); Wicherts et al. (2016)]. Existing research has already shown practices that reflect QMPs to be relatively common in both replication and original studies !!!CITE!!!. The purpose of this study is to provide a combined overview of the information on the reporting practices of measurement in replication and original with reliability and construct validity indices obtained from the shared item response data. By combining information on reporting with our own calculated indices, we can reflect on which validity issues lie in reporting and which are an issue with the measurement itself.

@@

One issue that has been observed with respect to measurement validation is that the reported measurement information is typically insufficient for readers to understand, evaluate, and reuse the measurement that was used [!!!CITE]. @flakeConstructValidityValidity2022 documented the measurement reporting practices among 100 replications and their respective original articles from the Reproducibility Project Psychology [@opensciencecollaborationEstimatingReproducibilityPsychological2015]. They coded the number of measures, the content of the measures, and information describing and justifying the measurement. They observed limited reporting of evidence demonstrating the reliability and validity of the measurement. Additionally, only eight of the 40 translated scales contained validity evidence for the translated version. A similar lack of reliability and validity reporting has been observed in other studies as well [@hoganEmpiricalStudyReporting2004; @flakeConstructValidationSocial2017]. If readers cannot glance the construct validity and reliability of a measure from the reported information, then readers lack the basic information needed to determine whether the measured variables are actually related to the constructs of interest. In turn, if we cannot determine whether the constructs of interest are captured in the measured variables or not, then the relation of the results of the statistical analysis using these variables and any psychological phenomena of interest is also strenuous. In short, if the reported information does not show that the measurement was valid, then any substantive conclusions from the data are unfortunately left unsubstantiated.

Further findings by @flakeConstructValidityValidity2022 and others [@flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020] show that measurement reporting was not only limited in terms of the reliability and validity evidence needed to evaluate the measure. The lack of information was also observed for basic content descriptions such as the number of items, the response format, and the scoring of the scale were irregular. This creates challenges for future researchers that want to reuse to measurement. Specifically for replication studies attempting to reconstruct the measurement from these incomplete descriptions, they may end up with a measurement that assesses the constructs in a substantially different way from the original study, or even assess different constructs altogether. If different constructs are assessed, the replication cannot be seen as a test of the same phenomenon as the original. If the same constructs are assessed, but in a substantially different way, the estimated effects in the replication cannot easily be put side-by-side with the effects in the original study. In either case, substantial comparisons between original and replication are hindered. The inability to reuse a measure does not only affect replications however, it also limits our ability to validate the measure thoroughly. Even if the measure is shown to be construct valid in one context, the factor relations may not be stable for this measure in other contexts and implementations, a concept known as measurement invariance [@hornPracticalTheoreticalGuide1992; @cheungDirectComparisonApproach2012]. While it is important to assess measurement (in)variance before using measures in a new context, if that measure is not reusable, the invariance cannot even be assessed.

Our first aim is to extend these existing findings on measurement reporting practices with a descriptive account of these practices for the Many Labs replications and the related original studies. We evaluate to what extent the reporting and use of item-based measurement scales in our sample allows us to evaluate and reuse the measurement. We do not ourselves evaluate whether the reported measurement information provide sufficient justification for its use, merely that information is reported such that that part of the measurement can be evaluated. We extend earlier investigations through new questions about the presence of justification for measurement selection or creation, item transformations such as reverse coding being described, the administration format being described, a change in the number of items from the source, whether changes in items response options, or number of items, or administration were validated or justified. All of our measurement reporting items were inspired by and categorized based on the QMP table in @flakeMeasurementSchmeasurementQuestionable2020.

We chose the Many Labs replications and associated original studies as our sample, due to them being of particular interest. The Many Labs replications were a series of large-scale collaborations in which multiple labs across the world directly replicated classic and contemporary psychological studies [@kleinInvestigatingVariationReplicability2014a; @ebersoleManyLabs32016; @kleinManyLabs22018b; @ebersoleManyLabs52020d; @kleinManyLabs42022]. The original studies chosen for replication in the Many Labs were not only picked based on ease and feasibility, but importantly for us they were also picked to display a diverse range of effects that were also of key interest to the field. This makes these studies an important sample to evaluate, because the replicated effects represent a broad range of relevant findings. Furthermore, because the Many Labs projects used preregistered and documented structured protocols, we expect the measurement reporting for the replications to represent a high standard within the field. Any issues in measurement reporting here might suggest that other replications could face similar or greater challenges.

@@

Psychometrics offers various ways in which to assess construct validity and reliability [@nunnallyOverviewPsychologicalMeasurement1978; @mellenberghConceptualIntroductionPsychometrics2011]. It is often the results from these psychometric analyses that form one of the pre-requisite pieces of evidence for assessing whether or not the measure is valid or not.

When psychometric indicators are reported - which as mentioned earlier is not common - it is often limited to Cronbach's Alpha, a commonly used indicator for reliability. Cronbach's Alpha comes with strong assumptions that are themselves rarely tested [@crutzenScaleQualityAlpha2017b]. Furthermore, research by @husseyAberrantAbundanceCronbachs2023 has shown evidence that the reporting of reliability may not only be little, but also biased. They observed a disproportional amount of Cronbach's Alpha values at the common acceptably reliable threshold value of .70, and relatively low reporting below .70. Thus, the lack of reported measurement evidence may on occasion be hiding psychometric skeletons in the closet.

As a result, if we want to evaluate the reliability of measurement in our sample, we cannot rely on the reported information alone to give us a representative picture. Thus, we evaluate the measurement reliability within the Many Labs original and replication studies by estimating it from the item response data. The data on the item responses are openly available per lab for our sample. As a result, we can evaluate not only the reliability per measure, but also the variation in reliability across labs. The variation is relevant because Cronbach's alpha is an indicator of reliability within a particular sample and not of the reliability of the measure in general, as it is proportional to the total variance in the target variable in the sample. Despite this many researchers report and interpret Cronbach's Alpha as a universal quality of the measure [@cortinaWhatCoefficientAlpha1993; @schmittUsesAbusesCoefficient1996]. @maireadshawMeasurementPracticesLargescale2020 has so far observed that for Many Labs 2 the overall sample Cronbach's alpha level across scales was below .5, a degree of reliability far below what many would consider acceptable for most research purposes. It is our second aim to empirically evaluate both the degree as well as the variation of reliability of the measures in our sample that includes the other Many Labs projects.

## Unidimensionality

Reliability is a pre-requisite to construct validity, because a measure for which a participant’s response is not consistent, cannot capture a stable construct [Kaplan and Saccuzzo (2013, pp. 154–155)]. Another, important pre-requisite for many measures is unidimensionality. Unidimensionality means that the items on a measure assess, show evidence of measuring a single construct. Thus, if a set of items are intended to measure the same one construct, then unidimensionality is key to the construct validity of that set of items. Additionally, most reliability indicators - including Cronbach's Alpha - cannot be assessed without first making sure that the measure is unidimensional. Thus for our third aim we again used the item response data. This time hitting two birds with one stone. We check the measures' construct validity, and we check if one of the key assumptions of Cronbach's Alpha is met.

!!!substantively belangrijk, want de scores worden als unidimensioneel geinterpreteerd. Alpha assumptie testen, als kleiner deel bespreken; Reliability kan in sommige gevallen slecht zijn als de schaal gewoon multi-dimensioneel is. Eerst een beetje techniek, daarna meer kwalitatief oordeel dat het gewoon belangrijk is voor interpretatie!!!

@maireadshawMeasurementPracticesLargescale2020 checked the factor structure on the openly available item data from Many Labs 2 [@kleinManyLabs22018b]. They observed that no scales in their sample did the results from the factor analysis meet all of their evaluation criteria for unidimensionality. @maireadshawMeasurementPracticesLargescale2020 had access to measures that were used across multiple contexts to evaluate their validity across more than one instance. However, in practice, measures are frequently made on the fly and reused maybe once or never [@weidmanJingleJangleEmotion2017; @elsonPsychologicalMeasuresArent2023; @anvariFragmentedFieldConstruct2025; @anvariDefragmentingPsychology2025]. This is dangerous, because these measures are often not validated before use, and if they cannot be reused, they are not going to be validated afterwards either. Furthermore, validating a scale requires substantial sample sizes in most cases [@maccallumSampleSizeFactor1999, @gorsuchFactorAnalysis2013], sample sizes that many original studies cannot obtain, in which case these measures are reliant on future research to obtain the required sample size to validate the measure.

Thus, for our third research aim - similarly to our aim with reliability - we check the unidimensionality of measures from the Many Labs projects per lab with meta-analytic assessment of the variation in unidimensionality across labs. The combined goal of our three research aims is to create a description of the measurement use in our data.

@@

We preregistered data collection, coding protocol, and planned analyses: <https://osf.io/jgxyu>. We deviated from our coding protocol as is explained further in the text. Our pre-registered analyses have been move to the [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_exploratory_version_pre-reg_analyses.Rmd) in favor of focusing on the descriptive results here.

@@

## Data Source

The data consists of three main sources: replication datasets, replication protocols, and original study articles. We retrieved the data of Many Labs 1, 2, 3, & 5 [@kleinInvestigatingVariationReplicability2014a; @ebersoleManyLabs32016; @kleinManyLabs22018b; @ebersoleManyLabs52020d] from their respective OSF pages. Many Labs 4 [@kleinManyLabs42022] was excluded, as there was no publicly available replication protocol. Additionally, the replication of [@crosbyWhereWeLook2008a] in Many Labs 5 made use of videos and eye-tracking measures, which did not match this study’s focus on item-based measures.

@@

Our unit of analysis is a measure of a single variable within a replication protocol or original article that was used in the main analysis that was replicated. For example, if conscientiousness and agreeableness were both measured using a big-five personality questionnaire, each of which was a variable in a replicated effect, then both the conscientiousness and agreeableness part of that questionnaire would be coded as their own unit of analysis. We also allowed for multiple variables to be measured per study. We used the replication protocols to identify the measure of each variable. We did not include acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses. Our final sample size was `r nrow(coded_data_replications)` measures of unique variables for both original and replication studies\^[Initially the original articles contained 3 more measures of unique variables than the replication protocols. This difference was due to the way that the moral foundations questionnaire was framed in the original article compared to in the replication protocol. In the original article it was framed as measuring five different moral foundations, while in the replication protocol the measure assessed the two overarching categories that were used to test the main effect in both the original and replication research. The measurement information reported was comparable across all five categories, and thus it was deemed that the measurement could be reduced to reflect two overarching categories facilitate easier comparison between measurement in original and replication.]

@@

The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>. Both the replication protocols and replication datasets were scanned through to ensure that they were the correct files to code measurement reporting information from. However, no coding or analysis of either of them had taken place before the analyses were preregistered. Further details on the search strategy can be found in the [coding protocol information file](../../SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd) in the supplementary materials.

@@

The replication datasets refer to the publicly available datasets containing the data obtained from all labs of each Many Labs replication. For the analyses, we extracted the scores on the items of each previously identified measure that also met our inclusion criteria specified in the paragraph below. When scores could not be clearly identified, any available codebooks, analysis scripts, or study materials were used to identify the relevant scores.

To be included in our reliability recalculations and factor analyses, the measure had to be a scale of multiple items. If cleaned data were available, we chose these over raw data, to ensure that variables were coded as intended (e.g., no reverse-coded items). We omitted pilot data from the analyses. These criteria combined with difficulties in retrieving suitable data from some datasets resulted in a set of item score data from `r length(unique(calculated_reliability_lab_data$g))` replication sets spread across on average approximately `r round(mean(table(calculated_reliability_lab_data$g)), 0)` lab locations for our analyses.

@@

The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of the replication of an original study. These were retrieved from the OSF pages of the Many Labs projects (the search strategy and OSF file locations can be found in the [data retrieval information](../../SupplementaryMaterials/data_retrieval_information.Rmd) supplementary document; URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/data_retrieval_information.Rmd>).

@@

### Coding Protocol

We extracted reported measurement information from the original articles and replication protocols using our preregistered coding protocol. We extracted the reported reliability coefficient and type of index (Cronbach’s Alpha, retest, interrater, etc.) when present. Similarly, we coded if any psychometric construct validity evidence, such as a factor analysis, was presented for the measure. We additionally included twenty items that were based on the QMP table presented in @flakeMeasurementSchmeasurementQuestionable2020. For each of these items we checked if a piece information we would want to see reported with regards to the measurement was described. If the information was clearly reported we coded the item as true; false if not or not clear enough; or not applicable if not relevant for that measure (e.g., reporting results from a factor analysis for single-item measures). Example items can be seen in Table \@ref(tab:QMPCodingInfoTable).

```{r QMPCodingInfoTable, warning = FALSE}
QMP_info_dataframe <- data.frame(Category = c("Definition", "", "", "Operationalisation", "", "", "", "Selection/Creation", "", "", "Quantification", "Modification", "", "", "", "", ""),
           'N Questions' = c("1", "", "", "5", "", "", "", "4", "", "", "4", "6", "", "", "", "", ""),
           'Example Question' = c("A psychological/sociological definition",
            "is given to the name of the measured",
            "variable within the paper.", 
            "The administration format (pen-and-",
            "paper/computer) and environment (in",
            "public/in a lab) are described (Note:",
            "both should be present for a true rating).", 
            "The source of the scale is provided",
            "(in case the scale was newly developed",
            "this should be clearly stated).", 
            "The number of items are described.", 
            "Any format changes are mentioned",
            "(paper-and-pencil <–> computer), if no",
            "changes were made to the format, and",
            "this was mentioned then code as No",
            "modification. If it is not clear, then code",
            "as False."))

# making the column names look less robot speak-y.
colnames(QMP_info_dataframe) <- c("Category", "N Questions", "Example Question")

# transfer the data to an APA table for printing
apa_table(
  QMP_info_dataframe, align = c("l", "r", "l")
  , caption = "Information of QMP coding variables per category."
  , note = "N Questions refers only to the questions used for calculating QMP ratios. Selection and creation share a category as the justifications and requirements in selecting a measure are similar to those for creating a new measure."
  , escape = FALSE, placement = "htp", booktabs = TRUE)

@@

After the initial coding, we made minor revisions to fourteen of the twenty QMP items from the preregistered coding protocol. These items were changed after familiarizing ourselves with the way measurement was reported, and it became clear that our criteria were too stringent in the exact way and degree of detail in which to present things. For example, in the initial protocol, an example item had to be present within the article or protocol itself, or else this was counted as a QMP. In the revised protocol, references to online appendices with example items were also considered sufficient for this item. The analyses, tables, and figures presented in this article are all based on the revised coding protocol. The equivalent QMP descriptives obtained with the initial protocol can be found in [Supplementary Analyses B](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_ratio_table.rmd).

>>>>

---
title             : "Measurement Reliability, Construct Validity, and Transparent Reporting in Original and Replication Research"
shorttitle        : "Measurement Reliability, Validity, and Reporting"

@@

abstract: |
  To assess psychological phenomena we need reliable and valid measurement of the construct(s) of interest. Information should therefore be reported alongside the measure to enable the evaluation of reliability and validity. Additionally, to ensure that reliable and valid measures can be reused in future research, the measure should be documented in sufficient detail. Therefore, we investigated the measurement reporting in a sample of 77 measures within 56 Many Labs replications and related original articles (Ebersole et al., 2016, 2020; Klein et al., 2014, 2018). We found that the information relevant for the reuse of a measure was reported in full for around half the replication measures, and only 5.2% of the original studies. We also observed that only around a third of multi-item measures in original studies and 11.4% in replications reported a reliability coefficient, with comparable proportions for reporting any psychometric validity evidence. Besides reporting, we also performed checks of the reliability and construct validity using the openly available Many Labs item response data. We observed that the reliability and construct validity of the measures was rarely stable across contexts. These results corroborate existing findings that measurement reporting in published research lacks transparency, and that this transparency may in certain contexts cover up insufficient reliability and valdity. Finally, we offer suggestions on how to increase measurement reporting transparancy and the use of validated measures.

keywords          : "reliability, construct validity, measurement, reporting, transparent reporting, replications, psychology"
wordcount         : "225"

@@

floatsintext      : yes
linenumbers       : yes
draft             : no
mask              : no

@@

csl               : "vancouver.csl"
documentclass     : "apa7"

@@

The challenge with measurement in quantitative psychological research is that unlike height or weight, psychological constructs cannot be directly measured, as they cannot be directly observed. Instead, we use scores from a measure as an indicator for a psychological construct. Yet, it cannot simply be assumed that any measure will form a good indicator of the constructs of interest. The measure has to be validated by establishing the reliability and construct validity of the measure. Following the definition of Crutzen and Peters, “[r]eliability refers to the consistency of scale scores when a construct is assessed multiple times or in multiple ways” [@crutzenScaleQualityAlpha2017b; pp. 244]. In turn, construct validity refers to whether the variance in the measured item scores between participants can be attributed to the variance in the unobserved construct(s) of interest between participants [@cronbachConstructValidityPsychological1955]. In practice, the measure itself is always validated within one or more use cases of a specific measurement procedure and the context in which that measurement took place, such as the sample characteristics, location, and time.

However, psychological measures often lack reliability and construct validity evidence, either because the evidence is not reported, or because the measures are not validated at all [@beckmanHowReliableAre2004; @barryValidityReliabilityReporting2014; @flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020; @flakeConstructValidityValidity2022]. Flake et al @flakeMeasurementSchmeasurementQuestionable2020 dubbed these such practices --- that raise doubts about the validity of a measurement --- “Questionable Measurement Practices” (QMPs), being a term analogous to Questionable Research Practices [QRPs; @simmonsFalsePositivePsychologyUndisclosed2011a; @johnMeasuringPrevalenceQuestionable2012a; @wichertsDegreesFreedomPlanning2016a]. A recent line of research has already shown QMPs to be relatively common in both original and replication psychology studies, damaging the trustworthiness and applicability of psychological research findings [@flakeConstructValidityValidity2022; @husseyAberrantAbundanceCronbachs2023].

The purpose of this study is to assess the measurement reporting practices of item-based measures in a diverse and seminal sample of original and replication studies in psychology. In addition, we will use the available item response data to calculate reliability and construct validity indices. Through the combination of assessing the measurement reporting and the calculated indices, we reflect on the apparent validity of the measurement based on the reported information, compared to the validity assessment when going beyond the reported information and checking the item response data.

@@

One issue that has been observed with respect to measurement validation is that the reported measurement information is typically insufficient for readers to understand, evaluate, and reuse the measurement that was used. Flake et al @flakeConstructValidityValidity2022 documented the measurement reporting practices among 100 original psychology articles and their respective replications from the Reproducibility Project Psychology [@opensciencecollaborationEstimatingReproducibilityPsychological2015]. They coded the number of measures, the content of the measures, and information describing and justifying the measurement. They observed limited reporting of evidence demonstrating the reliability and validity of the measurement. Additionally, only eight of the 40 translated scales contained validity evidence for the translated version. A similar lack of reliability and validity reporting has been observed in other studies as well [@hoganEmpiricalStudyReporting2004; @flakeConstructValidationSocial2017]. If readers cannot infer the construct validity and reliability of a measure from the reported information, then readers lack the basic information needed to determine whether the measured variables are actually related to the constructs of interest. In turn, if we cannot determine whether the constructs of interest are captured in the measured variables or not, then the relation of the results of the statistical analysis using these variables and any psychological phenomena of interest is also tenuous. In short, if the reported information does not show that the measurement was valid, then any substantive conclusions from the data are left unsupported.

Further findings by Flake et al @flakeConstructValidityValidity2022 and others [@flakeConstructValidationSocial2017; @maireadshawMeasurementPracticesLargescale2020] show that measurement reporting was not only limited in terms of the reliability and validity evidence. A lack of clearly reported information was also observed for basic content descriptions such as the number of items, the response format, and the scoring of the scale. This creates challenges for future researchers who want to reuse the measure to assess the same construct. Specifically, replication studies attempting to reconstruct the measurement from these incomplete descriptions may end up with a measurement that assesses the constructs in a substantially different way from the original study, or even assess different constructs altogether. If different constructs are assessed, the replication cannot be seen as a test of the same phenomenon as in the original study. If the same constructs are assessed, but in a substantially different way, the estimated effects in the replication cannot be easily compared to the effects in the original study. In either case, substantial comparisons between original and replication are hindered.

Our first aim is to extend the existing findings on measurement reporting practices with a descriptive account of these practices for the Many Labs replications and the related original studies. We will evaluate to what extent the reporting of item-based scales in our sample are transparent enough to facilitate the evaluation and reuse of these measurements. The Many Labs replications are a series of large-scale collaborations, in which multiple labs across the world directly replicated classic and contemporary psychological studies [@kleinInvestigatingVariationReplicability2014a; @ebersoleManyLabs32016; @kleinManyLabs22018b; @ebersoleManyLabs52020d; @kleinManyLabs42022]. The original studies chosen for replication in the Many Labs were not only picked based on feasibility, but importantly for us the sample of effects to replicate was chosen to contain a diverse range of seminal effects. Furthermore, because the Many Labs projects used preregistered and documented structured protocols, we expected the measurement reporting for the replications to represent a high standard within the field. Any issues in measurement reporting here might suggest that other replications could face similar or greater challenges.

@@

Two key aspects of measurement quality are reliability and construct validity. Psychometrics offers various methods for assessing these properties [@nunnallyOverviewPsychologicalMeasurement1978; @mellenberghConceptualIntroductionPsychometrics2011]. The results of such psychometric analyses often serve as essential evidence for evaluating a measure’s validity.

Reliability serves as a pre-requisite for a valid measure in most cases, because a measure for which a participant’s response is not consistent, cannot capture a stable construct [Kaplan and Saccuzzo (2013, pp. 154–155)]. It is therefore concerning that --- as mentioned earlier --- the reporting of psychometric indicators of reliability is not common, and is often limited to Cronbach’s Alpha. Unfortunate, because Cronbach’s Alpha comes with strong assumptions that are rarely tested [@crutzenScaleQualityAlpha2017b]. Furthermore, research by Hussey et al @husseyAberrantAbundanceCronbachs2023 has shown evidence that the reporting of reliability may not only be uncommon, but also biased. They observed a disproportional number of Cronbach’s Alpha values at the common acceptably reliability threshold value of .70, and relatively low reporting below .70. Thus, the lack of reported measurement evidence may indicate psychometric skeletons hiding in the closet.

As a result, if we want to evaluate the reliability of a measure in our sample, we cannot rely on the reported information alone to paint us a representative picture. Therefore, we also evaluated the measurement reliability within the Many Labs original and replication studies by estimating it from the item response data. The data on the item responses are openly available per lab for our sample. Therefore, we can evaluate not only the reliability per measure, but also the variation in reliability across labs. The variation is relevant because Cronbach’s Alpha is an indicator of reliability within a particular sample and not of the reliability of the measure in general, as it is proportional to the total variance in the target variable in the sample. Still, many researchers report and interpret Cronbach’s Alpha as a universal quality of the measure [@cortinaWhatCoefficientAlpha1993; @schmittUsesAbusesCoefficient1996]. @maireadshawMeasurementPracticesLargescale2020 have already observed that for Many Labs 2 the overall sample Cronbach’s Alpha level across scales was below .5, a degree of reliability far below what many would consider acceptable for most research purposes. Our second research aim is therefore to extend these findings by empirically evaluating both the degree as well as the variation of reliability of the measures in Many Labs projects 1, 2, 3, and 5.

## Construct Validity and Unidimensionality

Besides reliability, construct validity is key to establish for any measure. A multi-stage process is required to statistically and substantially establish a link between the measurement and the construct of interest. For example, the way a measure's items relate to each other and to the underlying concept (the factor relations) can differ substantially across contexts, a concept known as measurement invariance [@hornPracticalTheoreticalGuide1992; @cheungDirectComparisonApproach2012]. Thus, we cannot assume that the measure is valid in each context it is used in or meant to be used in, it is something that has to be established for each context. Besides investigating the factor structure, the measure should also be backed up substantively and logically [@borgstedeMeaningfulMeasurementRequires2023]. However, what we typically observe in psychological research is that measures are rarely substantiated with validity evidence [@beckmanHowReliableAre2004; @barryValidityReliabilityReporting2014; @flakeConstructValidationSocial2017; @flakeConstructValidityValidity2022]. This may in part be because the sample sizes required in validating a scale can often be larger than many studies are able to obtain [@maccallumSampleSizeFactor1999, @gorsuchFactorAnalysis2013]. Alternatively, researchers may not recognize measurement validation as part of their research method. Yet what has also been observed in the literature is that many measures are created ad hoc and reused maybe once or not at all [@weidmanJingleJangleEmotion2017; @elsonPsychologicalMeasuresArent2023; @anvariFragmentedFieldConstruct2025; @anvariDefragmentingPsychology2025]. This makes it extremely unlikely that the validity of these measure will ever be assessed at all, let alone be thoroughly investigated by analyzing measurement invariance across multiple groups using substantial sample sizes [@meadePowerPrecisionConfirmatory2007; @frenchMeasurementInvarianceTechniques2016; @koziolImpactModelParameterization2018].

One preliminary psychometric check that could easily be conducted is to see if the number of constructs measured by the items of the measurement match the intended number of constructs. Most often the scores on a measure or subscales of a measure are aggregated and interpreted as a singular index. In that case, the measure should be unidimensional. Otherwise, the researcher is interpreting a set of scores to be one concept when in fact they are multiple distinct concepts. Additionally, most reliability indicators --- including Cronbach’s Alpha --- cannot properly estimate true variance when it is spread across distinct constructs, and will thus give an inaccurate estimate of reliability [@schmittUsesAbusesCoefficient1996; @crutzenScaleQualityAlpha2017b].

Mairead shaw et al @maireadshawMeasurementPracticesLargescale2020 checked the dimensionality of the measurements from Many Labs 2 [@kleinManyLabs22018b], and while some support for unidimensionality was present, they found that none of the scales in their sample met all of their criteria for unidimensionality. Because the Many Labs replications reused existing measures across contexts, Mairead shaw et al @maireadshawMeasurementPracticesLargescale2020 could assess validity across contexts. Our third research aim is to extend these findings. We will perform our own checks of unidimensionality on measures from Many Labs 1, 2, 3, and 5 per lab, and include a meta-analytic assessment of the variation in unidimensionality across labs. The combined goal of our three research aims is to provide a descriptive account of the reliability, construct validity, and reporting of measurement in the included Many Labs study pairs.

@@

We preregistered data collection, coding protocol, and planned analyses: <https://osf.io/jgxyu>. We deviated from our coding protocol as is explained further in the text. The results from our preregistered analyses are described in [Supplementary Analyses A](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_exploratory_version_pre-reg_analyses.Rmd). In the main text, we focus on the descriptive results.

@@

## Data Source
The data consists of three main sources: replication datasets, replication protocols, and original study articles. We retrieved the data of Many Labs 1, 2, 3, & 5 [@kleinInvestigatingVariationReplicability2014a; @ebersoleManyLabs32016; @kleinManyLabs22018b; @ebersoleManyLabs52020d] from their respective OSF pages. Many Labs 4 [@kleinManyLabs42022] was excluded, as there were no publicly available replication protocols. Additionally, we excluded the replication of [@crosbyWhereWeLook2008a] in Many Labs 5, as it made use of videos and eye-tracking measures, which did not match this study’s focus on item-based measures.

@@

Our unit of analysis is a measure of a single variable within a replication protocol or original article that was used in the main analysis that was replicated. For example, if conscientiousness and agreeableness were both measured using the Big 5 Personality Test, each of which was a variable in a replicated effect, then both the conscientiousness and agreeableness part of that questionnaire would be coded as their own unit of analysis. We also allowed for multiple variables to be measured per study. We used the replication protocols to identify the measure of each variable. We did not include acquiescence bias checks, manipulation checks, pilot test measures, and measures added for exploratory analyses. Our final sample size was `r nrow(coded_data_replications)` measures of unique variables for both original and replication studies. Initially, the original articles contained 3 more measures of unique variables than the replication protocols. This difference was due to the way that the moral foundations questionnaire was framed in the original article compared to in the replication protocol. In the original article it was framed as measuring five different moral foundations, while in the replication protocol the measure assessed the two overarching categories that were used to test the main effect in both the original and replication research. The measurement information reported was comparable across all five categories, and thus it was deemed that the measurement could be reduced to reflect two overarching categories to facilitate easier comparison between measurement in original and replication.

@@

The data on the preregistered replication protocols, and replication datasets from Many Labs 1, 2, 3, & 5 were all retrieved from their respective OSF pages: <https://osf.io/wx7ck/>, <https://osf.io/8cd4r/>, <https://osf.io/ct89g/>, & <https://osf.io/7a6rd/>. We skimmed both the replication protocols and replication datasets to ensure that they were the correct files to code measurement reporting information from. However, no coding or analysis of either of them had taken place before the analyses were preregistered. Further details on the search strategy can be found in the [coding protocol information file](../../SupplementaryMaterials/CodingProtocols/coding_protocol_information.Rmd) in the supplementary materials.

@@

The replication datasets refer to the publicly available datasets containing the data obtained from all labs of each Many Labs replication. For the analyses, we extracted the scores on the items of each previously identified measure that also met our inclusion criteria specified in the paragraph below. When scores could not be clearly identified based on the information available in the dataset and the replication protocol, any available codebooks, analysis scripts, or study materials were used to identify the relevant scores.

To be included as part of the subset of measures we analyzed in our reliability recalculations and factor analyses, the measure had to be a scale of multiple items. If cleaned data were available, we chose these over raw data, to ensure that variables were coded as intended (e.g., no reverse-coded items). We omitted pilot data from the analyses. These criteria combined with our inability to definitively determine which variables in the dataset corresponded to the items on the measure of interest resulted in a set of item score data from `r length(unique(calculated_reliability_lab_data$g))` replication sets spread across on average approximately `r round(mean(table(calculated_reliability_lab_data$g)), 0)` lab locations for our analyses.

@@

The replication protocols refer to the publicly available protocols describing the background, methodology, and analysis of the replication of an original study. These were retrieved from the Open Science Framework (OSF) pages of the Many Labs projects (the search strategy and OSF file locations can be found in the [data retrieval information](../../SupplementaryMaterials/data_retrieval_information.Rmd) supplementary document; URL <https://github.com/CasGoos/measurement_and_replication/blob/master/SupplementaryMaterials/data_retrieval_information.Rmd>).

@@

### Measurement Reporting

We evaluated the transparency of the measurement reporting practices within the original articles and replication protocols using our preregistered coding protocol containing items assessing twenty three reporting practices. The items were based on Table \@ref(tab:QMPCodingInfoTable) presented in Flake et al @flakeMeasurementSchmeasurementQuestionable2020, listing what measurement information to report. We coded an item as “true” if the relevant measurement information was clearly reported, “false” if it was missing or unclear, and “not applicable” if it was irrelevant for that measure (e.g., reporting factor analysis results for single-item measures). These items thus indicate transparent reporting practices, which can be seen as the opposite of QMPs. We grouped the items into five categories, each representing a different element in measurement reporting. Example items are listed in Table \@ref(tab:QMPCodingInfoTable).

```{r QMPCodingInfoTable, warning = FALSE}
QMP_info_dataframe <- data.frame(Category = c("Definition", "", "", "Operationalisation", "", "", "", "", "Selection/Creation", "", "", "Quantification", "Modification", "", "", "", "", ""),
           'N Items' = c("1", "", "", "5", "", "", "", "", "7", "", "", "4", "6", "", "", "", "", ""),
           'Example Item' = c("A psychological/sociological definition",
            "is given to the name of the measured",
            "variable within the paper.", 
            "The administration format (pen-and-",
            "paper/computer) and environment (in",
            "public/in a lab) are described (Note:",
            "both should be present for this item to be", 
            "rated as “true”).", 
            "The source of the scale is provided",
            "(in case the scale was newly developed",
            "this should be clearly stated).", 
            "The number of items are described.", 
            "Any format changes are mentioned",
            "(paper-and-pencil <–> computer), if no",
            "changes were made to the format, and",
            "this was mentioned then code as No",
            "modification. If it is not clear, then code",
            "as False."))

# making the column names look less robot speak-y.
colnames(QMP_info_dataframe) <- c("Category", "N Items", "Example Item")

# transfer the data to an APA table for printing
apa_table(
  QMP_info_dataframe, align = c("l", "r", "l")
  , caption = "Example items used to code transparent measurement reporting practices across five categories linking to different aspects of measurement"
  , note = "Selection and creation of a measure share a category because the justifications and requirements in selecting a measure are similar to those for creating a new measure."
  , escape = FALSE, placement = "htp", booktabs = TRUE)

@@

Included within the list of measurement reporting information is crucially also the reported reliability coefficient and type of index (Cronbach’s Alpha, test-retest correlation, inter-rater reliability coefficient, etc.) when present. As well as the presence of any psychometric construct validity evidence for the measure, such as the results from a factor analysis.

After the initial coding, we made minor alterations from the preregistered coding protocol for fourteen of the twenty three measurement reporting practice items. These items were changed after familiarizing ourselves with the way measurement was reported, and it became clear that our criteria were too stringent. For example, in the initial protocol, an example item of the measure had to be present within the article or protocol itself, for the measurement practice to be considered clearly reported. In the revised protocol, references to online appendices with example items were also considered sufficient for this item. The analyses, tables, and figures presented in this article are all based on the revised coding protocol. The equivalent measurement reporting descriptives obtained with the initial protocol can be found in [Supplementary Analyses B](../../SupplementaryMaterials/SupplementaryAnalysesScripts/Supplementary_initial_QMP_ratio_table.rmd).
